Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-12 docs/thesis/chap-cern_math_explorer.tex
recursive interpretation subsection

\end{longtable}
\subsubsection{Recursive interpretation}

\subsubsection{Error handling}
Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} would be lost launching an exception and all following invocations would fail as well.
Also, re-instantiating a KernelLink would yield an Exception. For this scenario, killing the associated processes to Mathematica was necessary with {\codefont killall -s 9 Mathematica; killall -s 9 MathKernel
} or {\codefont taskkill /im Mathematica.exe; taskkill /im MathKernel.exe} depending on the OS the system is running on.

@@

\section{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
Our system is deployed as a standalone {\codefont jar} which is added to a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files}
The communication between Solr and Invenio was through the library {\codefont solrpy}. 
Figure \ref{system_arch} presents the main components of our deployment.

\begin{figure}
\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
\label{system_arch}
\caption{High level deployment architecture}
\end{figure}

@@

\begin{figure}
\includegraphics[height=8 cm]{figures/input_interface.png}
\label{input_int}
\caption{Web interface of $5e^{x+y}$: Query input screen}
\end{figure}

\begin{figure}
\includegraphics[height=8 cm]{figures/results_interface.png}
\label{results_int}
\caption{Web interface of $5e^{x+y}$: Results screen}
\end{figure}

>>>>

\end{longtable}
\subsubsection{Recursive interpretation}
Unfortunately, Mathematica cannot always interpret correctly an input expression. In this case, it can, however interpret some sub-expressions from the original one. Our system takes advantage of this, and the first attempt is to try to interpret the original string. If this step is not successful (the result variable equals the string "{}"), we identify the occurrences of {\codefont RowBox} which identify all the subexpressions in the tree. For each of this elements we call the {\codefont MakeExpression} and if it was successful we search for structural pattern in it. A first thought would tell us that if sub-tree was interpreted successfully, there is no need to try to go further down in that sub-tree, however, even if a sub-expression is interpreted correctly, the result sometimes is not complete and processing further down, gives better results. For this reason, we do not discard any of the subexpressions and try to interpret all of them. For this same reason, we do not store the number of occurrences of a given pattern, but only whether it contains is or not.

\subsubsection{Error handling}
Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} is lost and it launches an exception and all following invocations fail as well.
Also, re-instantiating a KernelLink would yield an Exception. For this scenario, killing the associated processes to Mathematica was necessary with {\codefont killall -s 9 Mathematica; killall -s 9 MathKernel
} or {\codefont taskkill /im Mathematica.exe; taskkill /im MathKernel.exe} depending on the OS the system is running on.

@@

\section{Integration with CDS}
Currently the Invenio code-base is being under a deep refactoring and rewriting. CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}. 
Our system is deployed as a standalone {\codefont jar} which is added to a Solr instance. Also, some extra configurations should be added. Details on this can be found in appendix \ref{appendix-conf_files}
The communication between Solr and Invenio was through the library {\codefont solrpy}. 
Figure 5.3 presents the main components of our deployment.

\begin{figure}[h!]
\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
\label{system_arch}
\caption{High level deployment architecture}
\end{figure}

@@

\begin{figure}
\center
\includegraphics[height=6.2 cm]{figures/input_interface.png}
\label{input_int}
\caption{Web interface of $5e^{x+y}$: Query input screen}
\end{figure}

\begin{figure}
\center
\includegraphics[height=6.2 cm]{figures/results_interface.png}
\label{results_int}
\caption{Web interface of $5e^{x+y}$: Results screen}
\end{figure}
